%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for USENIX papers.
%
% History:
%
% - TEMPLATE for Usenix papers, specifically to meet requirements of
%   USENIX '05. originally a template for producing IEEE-format
%   articles using LaTeX. written by Matthew Ward, CS Department,
%   Worcester Polytechnic Institute. adapted by David Beazley for his
%   excellent SWIG paper in Proceedings, Tcl 96. turned into a
%   smartass generic template by De Clarke, with thanks to both the
%   above pioneers. Use at your own risk. Complaints to /dev/null.
%   Make it two column with no page numbering, default is 10 point.
%
% - Munged by Fred Douglis <douglis@research.att.com> 10/97 to
%   separate the .sty file from the LaTeX source template, so that
%   people can more easily include the .sty file into an existing
%   document. Also changed to more closely follow the style guidelines
%   as represented by the Word sample file.
%
% - Note that since 2010, USENIX does not require endnotes. If you
%   want foot of page notes, don't include the endnotes package in the
%   usepackage command, below.
% - This version uses the latex2e styles, not the very ancient 2.09
%   stuff.
%
% - Updated July 2018: Text block size changed from 6.5" to 7"
%
% - Updated Dec 2018 for ATC'19:
%
%   * Revised text to pass HotCRP's auto-formatting check, with
%     hotcrp.settings.submission_form.body_font_size=10pt, and
%     hotcrp.settings.submission_form.line_height=12pt
%
%   * Switched from \endnote-s to \footnote-s to match Usenix's policy.
%
%   * \section* => \begin{abstract} ... \end{abstract}
%
%   * Make template self-contained in terms of bibtex entires, to allow
%     this file to be compiled. (And changing refs style to 'plain'.)
%
%   * Make template self-contained in terms of figures, to
%     allow this file to be compiled. 
%
%   * Added packages for hyperref, embedding fonts, and improving
%     appearance.
%   
%   * Removed outdated text.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix_2020_09}

% to be able to draw some self-contained figs
\usepackage{tikz}
\usepackage{amsmath}
%\usepackage[demo]{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

% inlined bib file
\usepackage{filecontents}

% add algorithm
%\usepackage{algorithm}
%\usepackage{algpseudocode}
%\usepackage[colorinlistoftodos]{todonotes}
%\usepackage{comment}
%\usepackage{gensymb}


%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

%don't want date printed
\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Is the Synthesized Scene in Autonomous Driving Realistic?}

%for single author (just remove % characters)
\author{
{\rm Elaine Yao}\\
University of British Columbia
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

\maketitle

%-------------------------------------------------------------------------------
 \begin{abstract}
%-------------------------------------------------------------------------------
\textbf{For Autonomous Vehicles(AVs), sensor perception is safety-critical. 
	Failures in object detection can cause disasters. 
	Despite various prior works on adversarial 3D physical attacks in AVs, all of them are simulating placing obstacles on the road with a synthesized scene.
	However, the rendering functions to generate the synthesized scenes may not be able to ensure the physical consistency between the obstacle and the background.
	The real-world sensor perception is much more complicated. In this project, we present the study of authenticity issues of rendering-based synthesized scenes in AV systems.
	We evaluate this by generating different synthesized scenes and testing the performance of the neural network on them.
	This allows us to quantify how realistic these scenes are and understand the impact of physical consistency in the scene on the effectiveness of generated adversarial objects.}


\textbf{We design a comprehensive test suite aiming at evaluating whether the method to integrate a 3D object in the road background is realistic or not.
	We adopt empirical approaches that address four main design challenges: 
	various impact factors, physical environment consistency, domain-specific metrics, and automated pipeline.
	We evaluate the synthesized scene with our test suite in representative open-source industry-grade AD system object detection models with real-world driving scenarios.
	We also choose a state-of-art adversarial 3D physical attack for evaluation in malicious cases.
	Our results show that most synthesized scenes are not realistic enough so the object detection fails to detect the obstacles in it.
	Such a phenomenon can reduce the effectiveness guarantee of generated 3D adversarial attacks in the physical world.}




 \end{abstract}


%-------------------------------------------------------------------------------
\section{Introduction}
%-------------------------------------------------------------------------------
\input{sections/introduction}

\section{Background}
\input{sections/background}

\section{Attack Model and Design Challenges}
\input{sections/attackmodel}

\section{Approach}
\input{sections/approach}

\section{Experiments}
\input{sections/experiments}

% \section{Discussions}
% \input{sections/discussion}

\section{Related Work}
\input{sections/related-work}


\bibliographystyle{plain}
\bibliography{refences}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%  LocalWords:  endnotes includegraphics fread ptr nobj noindent
%%  LocalWords:  pdflatex acks